\section{Exercise 2: Dependency checks and vectorization}

\begin{frame}{}
\begin{center}
{\Huge Exercise 2: Dependency checks and vectorization}\\\vspace{20pt}
{\Large Just a selection.}
\end{center}
\end{frame}

\begin{frame}{}
Complied with:
\begin{center}
icc -restrict -O3 -ipo -ip-no-inlining -qopt-report=3 -qopt-report-phase=vec vector.c
\end{center}
\end{frame}

\begin{frame}[fragile]{bsp1\_}
\begin{itemize}
\item Yes.
\item Masked assignment.
\end{itemize}
\begin{verbatim}
  for (i=0; i< n; i++) {
    if (x[i] > 0.) {
      e[i] = x[i] + y[i];
    } else {
      e[i] = x[i] - y[i];
    }
  }
\end{verbatim}
\end{frame}

\begin{frame}[fragile]{bsp2\_}
\begin{itemize}
\item Yes.
\item Exotically written loop, but still a loop!
\end{itemize}
\begin{verbatim}
  i = 0;
L10:
  /* Computing 3rd power */
  r1 = x[i] - y[i];
  e[i] = r1 * (r1 * r1);
  i++;
  if (i < n) {
    goto L10;
  }
\end{verbatim}
\end{frame}

\begin{frame}[fragile]{bsp4\_}
\begin{itemize}
\item Yes.
\item Read-after-write dependency, but offset is big enough!
\end{itemize}
\begin{verbatim}
  l = -100;
  for (i = n ; i < nn; i++) {
    x[i] = x[i + l];
  }
\end{verbatim}
\end{frame}

\begin{frame}[fragile]{bsp8\_}
\begin{itemize}
\item No. Or maybe little bit?
\item Non-unit strided access to \texttt{x}, \texttt{z} and \texttt{y}.
\item Indirect addressing.
\item Still the compiler managed to vectorize this through emulation of non-unit strided and irregularly indexed loads. Estimated potential speedup: 1.44
\end{itemize}
\begin{verbatim}
  for (i=0; i < n; i++) {
    x[i] = x[i * 2] + z[i + i];
    e[i] = y[i] + y[iy[i] * iy[i]];
  }
\end{verbatim}
\end{frame}

\begin{frame}[fragile]{bsp12\_}
\begin{itemize}
\item Yes.
\item Original order of nested loops results in non-unit strided access. However compiler can interchange the order of both loops.
\end{itemize}
\begin{verbatim}
  for (j=0; j < n; j++) {
    for (i=0; i < n-1; i++) {
      a[i+1][j] = a[i][j] * b[i][j];
    }
  }
\end{verbatim}
\end{frame}

\begin{frame}[fragile]{bsp17\_}
\begin{itemize}
\item Normally not.
\item There is a write-after-write dependency in \texttt{s} that would normally prohibit vectorization.
\item However the compiler detects this reduction idiom and safely vectorizes the loop.
\end{itemize}
\begin{verbatim}
  *s = 0.;
  for (i = 0; i < n; i++) {
    *s += x[i];
  }
\end{verbatim}
\end{frame}

\begin{frame}{Improving the code}
\begin{itemize}
\item Arrays have been declared with \texttt{\_\_declspec(align(16))}.
\item Declaring \texttt{f\_()} as \texttt{inline} facilitates vectorization of \texttt{bsp10\_}
\end{itemize}
\end{frame}
